Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-06-21 paper.tex
fixed references
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\section{New Applications: Beyond Code Correctness}
\label{Newapp}

As already mentioned in section \ref{sec:model}, problems that are not directly related to code correctness may be tackled with formal methods, as long as the are conveniently modeled. Ara\'ujo {\it et. al} \cite{Araujo16} employed SMT for handling non-convex optimization problems, with the goal of ensuring optimal solutions. Indeed, it is possible to recursively re-constrains a model checking procedure, by using the current counterexample as a seed for the next run, until a global minimum is achieved. Nonetheless, the elapsed execution time is still a bottleneck for some applications, such as changes in UAV trajectory, but that can be improved, through the use of simplification techniques and and problem constraints.

In the same fashion, other problems may benefit from the recursive-refinement approach provided by SMT-based verification schemes. For instance, de Jesus {\it et. al} \cite{antennasbrt} developed a simplified methodology for antenna alignment that makes use of many modules already available in satellite TV receivers, along with a suitable structure for performing position correction. In summary, a reference signal is evaluated, until an (approximately) error-free reception is acquired, which can be measured through a simple transport stream (TS) error-indication interface and further refined with other parameters, such as carrier-to-noise ratio and signal level. This way, by using an SMT-based verification method, one may map the TS error indication and other performance figures as properties and then recursively perform realignments procedures, until a counterexample is not output. It is worth noticing that the timing requirements are more relaxed than what was mentioned in the work developed by Ara\'ujo {\it et. al} \cite{Araujo16}, which can be seen as an advantage for such an implementation.

Regarding behavior correctness, many other applications can be tackled, such as the ones related to automatic classification. Amoedo {\it et. al} proposed a modulation classification methodology, which the goal of spectrum sensing for opportunistic transmissions. Given that 
%--------------------------------------
\section{Conclusions}
\label{conclusions}
%--------------------------------------

@@

\bibitem{ldd}
Witkowski T., Blanc N., Kroening D., Weissenbacher G.:
\newblock {\em {Model checking concurrent linux device drivers}}.
\newblock In: 22nd IEEE/ACM international conference on Automated software engineering, pp. 501--504, 2007.

%9
\bibitem{mlembe}
S.~Virtanen:
\newblock {\em {Advancing Embedded Systems and Real-Time Communications with Emerging Technologies}}.
\newblock IGI Global, ISBN 978-1466660342, pp. 1--502, 2014.

%10
\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em {Effective Verification of Low-Level Software with Nested Interrupts}}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

%11
\bibitem{cudalucas}
Monteiro F. R., da Silva Alves E. H., Silva I. S., Ismail H., Cordeiro L. C., de Lima Filho E. B.:
\newblock {\em {ESBMC-GPU A Context-Bounded Model Checking Tool to Verify CUDA Programs}}. 
\newblock In: Science of Computer Programming xx(y): pp. xxxx--xxxx, 2017.

%12
\bibitem{stochmodel}
Bargmann H.:
\newblock {\em {The role of stochastic modelling in engineering science}}.
\newblock In: Acta Mecanica 125(1), pp. 63--71, 1997.

%13
\bibitem{Shoukry}
Shoukry Y., Nuzzo P., Puggelli A., Sangiovanni-Vincentelli A. L., Seshia S. A., Tabuada P.:
\newblock {\em {Secure State Estimation for Cyber Physical Systems Under Sensor Attacks: A Satisfiability Modulo Theory Approach}}.
\newblock {IEEE} Trans. Automatic Control PP(99), pp. 1--16, 2017.

%14
\bibitem{cpsattack}
Liu Y., Ning P., Reiter M. K.:
\newblock {\em {“False data injection attacks against state estimation in electric power grid}}.
\newblock In: ACM Conference on Computer and Communications Security, pp. 21--32, 2009.

%15
\bibitem{Araujo16}
Araujo, R., Bessa, I., Cordeiro, L., Chaves Filho, J.:
\newblock {\em{ SMT-based Verification Applied to Non-convex Optimization Problems}}. 
\newblock In: VI Brazilian Symposium on Computing Systems Engineering, 2016 (to appear).

%16
\bibitem{Biere99}
Biere A., Cimatti A., Clarke E., Zhu Y.:
\newblock {\em {Symbolic Model Checking without BDDs}}. 
\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.

%17
\bibitem{handbook09}
Biere A., Heule M., van Maaren H., Walsh T., eds.:
\newblock {\em {Handbook of Satisfiability}}.
\newblock Volume 185 of Frontiers in Artificial Intelligence and Applications., {IOS} Press, 2009.

%18
\bibitem{BarrettSST09}
Barrett C., Sebastiani R., Seshia S.A., Tinelli C.:
\newblock {\em {Satisfiability Modulo Theories}}. 
\newblock In: Volume 185 of Frontiers in Artificial Intelligence and Applications. IOS Press, pp. 825--885, 2009.

%19
\bibitem{Armando06}
Armando A., Mantovani J., Platania L.:
\newblock {\em {Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}}. 
\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.

%20
\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em {A Tool for Checking {ANSI-C} Programs}}.
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg, pp. 168--176, 2004.

%21
\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {{LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}}}.
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

%22
\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em {Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking}}.
\newblock In: International Conference on Software Engineering. pp. 331--340, 2011.

%23
\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em {Model Checking {C} Programs using {F-Soft}}}.
\newblock In: International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

%24
\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {{SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}}.
\newblock {IEEE} Trans. Software Eng. 38(4), pp. 957--974, 2012.

%25
\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em {Temporal Induction by Incremental {SAT} Solving}}.
\newblock Electronic Notes in Theoretical Computer Science 89(4), pp. 543 -- 560, 2003.

%26
\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em {Checking Safety Properties using Induction and a {SAT}-solver}}.
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

%27
\bibitem{Bradley07}
Bradley A., Manna Z.:
\newblock {\em {The calculus of computation - decision procedures with applications to verification}}. 
\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.

%28
\bibitem{4610935}
{IEEE} standard for floating-point arithmetic.
\newblock {\em IEEE Std 754-2008}, pages 1--70, Aug 2008.

%29
\bibitem{Goldberg91whatevery}
David Goldberg.
\newblock What every computer scientist should know about floating point
  arithmetic.
\newblock {\em ACM Computing Surveys}, 23(1):5--48, 1991.

%30
\bibitem{pips:2013}
ParisTech M.:
\newblock {\em {PIPS: Automatic Parallelizer and Code Transformation Framework}}. 
\newblock Accessed 21 February 2016

%31
\bibitem{Henry:2012}
Henry J., Monniaux D., Moy M.: 
\newblock {\em {PAGAI: A Path Sensitive Static Analyser}}. 
\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.

%32
\bibitem{Beyer15}
Beyer D., Dangl M., Wendler P.:
\newblock {\em {Boosting \textit{k}-Induction with Continuously-Refined Invariants}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 9206, pp. 622--640, 2015.

%33
\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em {Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction}}.
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

%34
\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em {Safety Verification and Refutation by k-Invariants and \textit{k}-Induction}}.
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

%35
\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em {Model Checking Embedded C Software using \textit{k}-Induction and Invariants}}.
\newblock In: V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

%36
\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em {Software Verification using \textit{k}-Induction}}.
\newblock In: International Symposium on Static Analysis. LNCS 6887, pp. 351--368, 2011.

%37
\bibitem{Rocha17}
Rocha, W., Rocha, H., Ismail H., Cordeiro, L., Fischer, B.:
\newblock {\em {DepthK: A \textit{k}-Induction Verifier Based on Invariant Inference for C Programs}}. 
\newblock In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems, 2017 (to appear).

%38
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {{SCRATCH}: A Tool for Automatic Analysis of {DMA} Races}}.
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%39
\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em {Induction-based Formal Verification of {SystemC TLM} Designs}}.
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

%40
\bibitem{David15}
C.~David, D.~Kroening, and M.~Lewis.
\newblock {\em {Using program synthesis for program analysis}}.
\newblock In: Logic for Programming, Artificial Intelligence, and Reasoning, LNCS 9450, pp. 483--498, 2015.

%41
\bibitem{Alur13}
Alur R., Bod\'{\i}k R., Juniwal G., Martin M., Raghothaman M., Seshia S., Singh R., Solar-Lezama A., Torlak E., Udupa A.:
\newblock {\em {Syntax-guided synthesis}}. 
\newblock In: Formal Methods in Computer-Aided Design, pp. 1--8, 2013.

%42
\bibitem{sketch}
A.~Solar-Lezama.
\newblock {\em {Program sketching}}.
\newblock In: International Journal on Software Tools for Technology Transfer, 15(5-6):475--495, 2013.

%43
\bibitem{Sharma14}
R.~Sharma and A.~Aiken.
\newblock {\em {From invariant checking to invariant inference using randomized search}}.
\newblock In: Computer Aided Verification, LNCS 8559, pp. 88--105, 2014.

%44
\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em {DSVerifier: A Bounded Model Checking Tool for Digital Systems}}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

%45
\bibitem{Monteiro16}
F.~Monteiro:
\newblock {\em {Bounded model checking of state-space digital systems: the impact of finite word-length effects on the implementation of fixed-point digital controllers based on state-space modeling}}. 
\newblock In: 24th {ACM} {SIGSOFT} International Symposium on Foundations of Software Engineering, pp. 1151--1153, 2016.

%46
\bibitem{Bessa17}
Bessa, I., Ismail, H., Palhares, R., Cordeiro, L., Chaves Filho, J.:
\newblock {\em {Formal Non-Fragile Stability Verification of Digital Control Systems with Uncertainty}}. 
\newblock In: IEEE Transactions on Computers, 2017 (to appear).

%47
\bibitem{selfcar}
Fairley P.:
\newblock {\em {Self-Driving Cars Have a Bicycle Problem}}.
\newblock http://spectrum.ieee.org/transportation/self-driving/selfdriving-cars-have-a-bicycle-problem.

%48
\bibitem{BMCml}
L.~Bortolussi, D. Milios, G, Sanguinetti.:
\newblock {\em {Smoothed model checking for uncertain Continuous-Time Markov Chains}}.
\newblock In:. Information and Computation, 2016.

%49
\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em {Scalable and Optimized Hybrid Verification of Embedded Software}}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

%50
\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em {Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

%51
\bibitem{Adouane16}
Vilca J., Adouane L., Mezouar Y.:
\newblock {\em {Optimal Multi-Criteria Waypoint Selection for Autonomous Vehicle Navigation in Structured Environment}}. 
\newblock In: Journal of Intelligent and Robotic Systems 82(2): pp. 301--324, 2016.

%52
\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

%53
\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em {Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking}}.
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

%54
\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

%55
\bibitem{Beyer14}
D.~Beyer 
\newblock {\em {Status report on software verification - (competition summary {SV-COMP})}}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.

%56
\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em {Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).}} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

%57
\bibitem{KahlonWG09}
Kahlon V., Wang C., Gupta A.:
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%58
\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

%59
\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em {Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.

%60
\bibitem{civl15}
Zheng M, Rogers M, Luo Z, Dwyer M, Siegel S.
\newblock {\em{{CIVL}: Formal Verification of Parallel Programs}}.
\newblock In: International Conference on Automated Software Engineering, pp. 830--835, 2015.

%61
\bibitem{Grumberg05}
Grumberg O., Lerda F., Strichman O., Theobald M.:
\newblock {\em { Proof-guided underapproximation-widening for multi-process systems.}} 
\newblock In: Symposium on Principles of Programming Languages, pp. 122--131, 2005.

%62
\bibitem{McMillan11}
K.~McMillan:
\newblock {\em {Widening and Interpolation.}} 
\newblock In: International Symposium on Static Analysis, LCNS 6887, pp. 1, 2011.

%63
\bibitem{esbmc_controller}
Bessa I., Abreu R., Cordeiro L., Filho J.:
\newblock {\em {SMT-Based Bounded Model Checking of Fixed-Point Digital Controllers}.}
\newblock In: Annual Conference of the Industrial Electronics Society, pp. 295--301, 2014.

>>>>

%----------------------------------------------------------------------------
\section{New Applications: Beyond Code Correctness}
\label{Newapp}
%----------------------------------------------------------------------------

As already mentioned in section \ref{sec:model}, problems that are not directly related to code correctness may be tackled with formal methods, as long as they are conveniently modeled. Ara\'ujo {\it et al.} \cite{Araujo16} employed SMT for handling non-convex optimization problems, with the goal of ensuring optimal solutions. Indeed, it is possible to recursively re-constrains a model checking procedure, by using the current counterexample as a seed for the next run, until a global minimum is achieved. Nonetheless, the elapsed execution time is still a bottleneck for some applications, such as changes in UAV trajectory, but that can be improved, through the use of simplification techniques and problem constraints.

In the same fashion, other problems may benefit from the recursive-refinement approach provided by SMT-based verification schemes. For instance, de Jesus {\it et. al} \cite{antennasbrt} developed a simplified methodology for antenna alignment that makes use of many modules already available in satellite TV receivers, along with a suitable structure for performing position correction. In summary, a reference signal is evaluated, until an (approximately) error-free reception is acquired, which can be measured through a simple transport stream (TS) error-indication interface and further refined with other parameters, such as carrier-to-noise ratio and signal level. This way, by using an SMT-based verification method, one may map the TS error indication and other performance figures as properties and then recursively perform realignments procedures, until a counterexample is not output. It is worth noticing that the timing requirements are more relaxed than what was mentioned in the work developed by Ara\'ujo {\it et al.}~\cite{Araujo16}, which can be seen as an advantage for such an implementation.

Regarding behavior correctness, many other applications can be tackled, such as the ones related to automatic classification. Amoedo {\it et al.} proposed a modulation classification methodology, which the goal of spectrum sensing for opportunistic transmissions. Given that

\textcolor{red}{Eddie: Acho que esta faltando texto aqui, certo?}
%--------------------------------------
\section{Conclusions}
\label{conclusions}
%--------------------------------------

@@

%9
\bibitem{ldd}
Witkowski T., Blanc N., Kroening D., Weissenbacher G.:
\newblock {\em {Model checking concurrent linux device drivers}}.
\newblock In: 22nd IEEE/ACM international conference on Automated software engineering, pp. 501--504, 2007.

%10
\bibitem{mlembe}
S.~Virtanen:
\newblock {\em {Advancing Embedded Systems and Real-Time Communications with Emerging Technologies}}.
\newblock IGI Global, ISBN 978-1466660342, pp. 1--502, 2014.

%11
\bibitem{Kroening15}
Kroening D., Liang L., Melham T., Schrammel P., Tautschnig M.:
\newblock {\em {Effective Verification of Low-Level Software with Nested Interrupts}}. 
\newblock In: Design, Automation and Test in Europe, pp. 229--234, 2015.

%12
\bibitem{cudalucas}
Monteiro F. R., da Silva Alves E. H., Silva I. S., Ismail H., Cordeiro L. C., de Lima Filho E. B.:
\newblock {\em {ESBMC-GPU A Context-Bounded Model Checking Tool to Verify CUDA Programs}}. 
\newblock In: Science of Computer Programming xx(y): pp. xxxx--xxxx, 2017.

%13
\bibitem{stochmodel}
Bargmann H.:
\newblock {\em {The role of stochastic modelling in engineering science}}.
\newblock In: Acta Mecanica 125(1), pp. 63--71, 1997.

%14
\bibitem{Shoukry}
Shoukry Y., Nuzzo P., Puggelli A., Sangiovanni-Vincentelli A. L., Seshia S. A., Tabuada P.:
\newblock {\em {Secure State Estimation for Cyber Physical Systems Under Sensor Attacks: A Satisfiability Modulo Theory Approach}}.
\newblock {IEEE} Trans. Automatic Control PP(99), pp. 1--16, 2017.

%15
\bibitem{cpsattack}
Liu Y., Ning P., Reiter M. K.:
\newblock {\em {“False data injection attacks against state estimation in electric power grid}}.
\newblock In: ACM Conference on Computer and Communications Security, pp. 21--32, 2009.

%16
\bibitem{Araujo16}
Araujo, R., Bessa, I., Cordeiro, L., Chaves Filho, J.:
\newblock {\em{ SMT-based Verification Applied to Non-convex Optimization Problems}}. 
\newblock In: VI Brazilian Symposium on Computing Systems Engineering, 2016 (to appear).

%17
\bibitem{Biere99}
Biere A., Cimatti A., Clarke E., Zhu Y.:
\newblock {\em {Symbolic Model Checking without BDDs}}. 
\newblock In: Tools and Algorithms for Construction and Analysis of Systems, LNCS 1579, pp. 193--207, 1999.

%18
\bibitem{handbook09}
Biere A., Heule M., van Maaren H., Walsh T., eds.:
\newblock {\em {Handbook of Satisfiability}}.
\newblock Volume 185 of Frontiers in Artificial Intelligence and Applications., {IOS} Press, 2009.

%19
\bibitem{BarrettSST09}
Barrett C., Sebastiani R., Seshia S.A., Tinelli C.:
\newblock {\em {Satisfiability Modulo Theories}}. 
\newblock In: Volume 185 of Frontiers in Artificial Intelligence and Applications. IOS Press, pp. 825--885, 2009.

%20
\bibitem{Armando06}
Armando A., Mantovani J., Platania L.:
\newblock {\em {Bounded Model Checking of Software Using SMT Solvers Instead of SAT Solvers}}. 
\newblock In: {SPIN} Workshop on Model Checking Software, LNCS 3925, pp. 146-162, 2006.

%21
\bibitem{Bradley07}
Bradley A., Manna Z.:
\newblock {\em {The calculus of computation - decision procedures with applications to verification}}. 
\newblock In: Springer, pp. I-XV, pp. 1--366, 2007.

%22
\bibitem{Thomas01}
Thomas Ball and Sriram~K. Rajamani.
\newblock {\em SLIC: A Specification Language for Interface Checking (of C)}.
\newblock Technical Report MSR-TR-2001-21, Microsoft Research, 2001.

%23
\bibitem{Strichman08}
Daniel Kroening and Ofer Strichman.
\newblock {\em Decision Procedures: An Algorithmic Point of View}.
\newblock Springer Publishing Company, Incorporated, 2008.

%24
\bibitem{Appel97}
Andrew~W. Appel.
\newblock {\em Modern Compiler Implementation in C: Basic Techniques}.
\newblock Cambridge University Press, New York, NY, USA, 1997.

%25
\bibitem{Tseitin83}
G.~S. Tseitin.
\newblock On the complexity of derivation in propositional calculus.
\newblock In {\em In J. Siekmann and G. Wrightson, editors, Automation of
  Reasoning 2: Classical Papers on Computational Logic 1967-1970}.

 %26
 \bibitem{PatarinG97}
Jacques Patarin and Louis Goubin.
\newblock Trapdoor one-way permutations and multivariate polynominals.
\newblock In {\em ICICS}, {\em LNCS} 1334, pages 356--368. Springer, 1997.

%27
\bibitem{Clarke04}
Clarke E., Kroening D., Lerda F.:
\newblock {\em {A Tool for Checking {ANSI-C} Programs}}.
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems. LNCS 2988, Springer Berlin Heidelberg, pp. 168--176, 2004.

%28
\bibitem{MerzFS12}
Merz F., Falke S., Sinz C.:
\newblock {\em {{LLBMC}: Bounded Model Checking of {C} and {C++} Programs using a Compiler {IR}}}.
\newblock In: International Conference on Verified Software: Theories, Tools, Experiments. LNCS 7152, pp. 146--161, 2012.

%29
\bibitem{CordeiroF11}
Cordeiro L., Fischer B.:
\newblock {\em {Verifying Multi-threaded Software using {SMT}-based Context-Bounded Model Checking}}.
\newblock In: International Conference on Software Engineering. pp. 331--340, 2011.

%30
\bibitem{Ivancic05}
Ivanicic F., Shlyakhter I., Gupta A., Ganai, M.K.:
\newblock {\em {Model Checking {C} Programs using {F-Soft}}}.
\newblock In: International Conference on Computer Design: VLSI in Computers and Processors, pp. 297--308, 2005.

%31
\bibitem{Cordeiro12}
Cordeiro L., Fischer B., Marques{-}Silva J.:
\newblock {\em {{SMT}-based Bounded Model Checking for Embedded {ANSI-C} Software}}.
\newblock {IEEE} Trans. Software Eng. 38(4), pp. 957--974, 2012.

%32
\bibitem{EenS03}
E{\'{e}}n, N., S{\"{o}}rensson, N.:
\newblock {\em {Temporal Induction by Incremental {SAT} Solving}}.
\newblock Electronic Notes in Theoretical Computer Science 89(4), pp. 543 -- 560, 2003.

%33
\bibitem{Sheera00}
Sheeran M., Singh S., St{\aa}lmarck G.:
\newblock {\em {Checking Safety Properties using Induction and a {SAT}-solver}}.
\newblock In: International Conference on Formal Methods in Computer-Aided Design. Springer-Verlag, pp. 108--125, 2000.

%34
\bibitem{4610935}
{IEEE} standard for floating-point arithmetic.
\newblock {\em IEEE Std 754-2008}, pages 1--70, Aug 2008.

%35
\bibitem{Goldberg91whatevery}
David Goldberg.
\newblock What every computer scientist should know about floating point
  arithmetic.
\newblock {\em ACM Computing Surveys}, 23(1):5--48, 1991.

%36
\bibitem{pips:2013}
ParisTech M.:
\newblock {\em {PIPS: Automatic Parallelizer and Code Transformation Framework}}. 
\newblock Accessed 21 February 2016

%37
\bibitem{Henry:2012}
Henry J., Monniaux D., Moy M.: 
\newblock {\em {PAGAI: A Path Sensitive Static Analyser}}. 
\newblock In: Electronic Notes in Theoretical Computer Science, pp. 15--25, 2012.

%38
\bibitem{Beyer15}
Beyer D., Dangl M., Wendler P.:
\newblock {\em {Boosting \textit{k}-Induction with Continuously-Refined Invariants}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 9206, pp. 622--640, 2015.

%39
\bibitem{Gadelha15}
Gadelha M., Ismail H., Cordeiro L.:
\newblock {\em {Handling Loops in Bounded Model Checking of C Programs via \textit{k}-Induction}}.
\newblock In: International Journal on Software Tools for Technology Transfer (to appear), 2015.
\newblock http://dx.doi.org/10.1007/s10009-015-0407-9

%40
\bibitem{Brain15}
Brain M., Joshi S., Kroening D., Schrammel P.:
\newblock {\em {Safety Verification and Refutation by k-Invariants and \textit{k}-Induction}}.
\newblock In: International Symposium on Static Analysis, LNCS 9291, pp. 145--161, 2015.

%41
\bibitem{Rocha15}
Rocha H., Ismail H., Cordeiro L., Barreto R.:
\newblock {\em {Model Checking Embedded C Software using \textit{k}-Induction and Invariants}}.
\newblock In: V Brazilian Symposium on Computing Systems Engineering, pp. 90--95, 2015.

%42
\bibitem{Kinductor}
Donaldson A., Haller L., Kroening D., R{\"{u}}mmer, P.:
\newblock {\em {Software Verification using \textit{k}-Induction}}.
\newblock In: International Symposium on Static Analysis. LNCS 6887, pp. 351--368, 2011.

%43
\bibitem{Rocha17}
Rocha, W., Rocha, H., Ismail H., Cordeiro, L., Fischer, B.:
\newblock {\em {DepthK: A \textit{k}-Induction Verifier Based on Invariant Inference for C Programs}}. 
\newblock In: International Conference on Tools and Algorithms for the Construction and Analysis of Systems, 2017 (to appear).

%44
\bibitem{Donaldson10}
Donaldson A., Kroening D., R{\"{u}}mmer P.:
\newblock {\em {{SCRATCH}: A Tool for Automatic Analysis of {DMA} Races}}.
\newblock In: ACM Symposium on Principles and Practice of Parallel Programming. ACM, pp. 311--312, 2011.

%45
\bibitem{GrosseLD09}
Gro{\ss}e D., Le H., Drechsler R.:
\newblock {\em {Induction-based Formal Verification of {SystemC TLM} Designs}}.
\newblock In: International Workshop on Microprocessor Test and Verification, pp. 101--106, 2009.

%46
\bibitem{David15}
C.~David, D.~Kroening, and M.~Lewis.
\newblock {\em {Using program synthesis for program analysis}}.
\newblock In: Logic for Programming, Artificial Intelligence, and Reasoning, LNCS 9450, pp. 483--498, 2015.

%47
\bibitem{Alur13}
Alur R., Bod\'{\i}k R., Juniwal G., Martin M., Raghothaman M., Seshia S., Singh R., Solar-Lezama A., Torlak E., Udupa A.:
\newblock {\em {Syntax-guided synthesis}}. 
\newblock In: Formal Methods in Computer-Aided Design, pp. 1--8, 2013.

%48
\bibitem{sketch}
A.~Solar-Lezama.
\newblock {\em {Program sketching}}.
\newblock In: International Journal on Software Tools for Technology Transfer, 15(5-6):475--495, 2013.

%49
\bibitem{Sharma14}
R.~Sharma and A.~Aiken.
\newblock {\em {From invariant checking to invariant inference using randomized search}}.
\newblock In: Computer Aided Verification, LNCS 8559, pp. 88--105, 2014.

%50
\bibitem{dsv_spin2015}
Ismail H., Bessa I., Cordeiro L., Lima Filho E., Chaves Filho J.:
\newblock {\em {DSVerifier: A Bounded Model Checking Tool for Digital Systems}}. 
\newblock In: International SPIN Symposium on Model Checking of Software, LNCS 9232, pp. 126--131, 2015.

%51
\bibitem{Monteiro16}
F.~Monteiro:
\newblock {\em {Bounded model checking of state-space digital systems: the impact of finite word-length effects on the implementation of fixed-point digital controllers based on state-space modeling}}. 
\newblock In: 24th {ACM} {SIGSOFT} International Symposium on Foundations of Software Engineering, pp. 1151--1153, 2016.

%52
\bibitem{Bessa17}
Bessa, I., Ismail, H., Palhares, R., Cordeiro, L., Chaves Filho, J.:
\newblock {\em {Formal Non-Fragile Stability Verification of Digital Control Systems with Uncertainty}}. 
\newblock In: IEEE Transactions on Computers, 2017 (to appear).

%53
\bibitem{selfcar}
Fairley P.:
\newblock {\em {Self-Driving Cars Have a Bicycle Problem}}.
\newblock http://spectrum.ieee.org/transportation/self-driving/selfdriving-cars-have-a-bicycle-problem.

%54
\bibitem{BMCml}
L.~Bortolussi, D. Milios, G, Sanguinetti.:
\newblock {\em {Smoothed model checking for uncertain Continuous-Time Markov Chains}}.
\newblock In:. Information and Computation, 2016.

%55
\bibitem{Behrend15}
Behrend J., Lettnin D., Gruenhage A., Ruf J., Kropf T., Rosenstiel W.:
\newblock {\em {Scalable and Optimized Hybrid Verification of Embedded Software}}. 
\newblock In: J. Electronic Testing 31(2): pp. 151--166, 2015.

%56
\bibitem{Lettnin09}
Lettnin D., Nalla P. K., Behrend J., Ruf J., Gerlach J., Kropf T., Rosenstiel W., Sch{\"o}nknecht V., Reitemeyer S.:
\newblock {\em {Semiformal Verification of Temporal Properties in Automotive Hardware Dependent Software}}. 
\newblock In: Design, Automation and Test in Europe, pp. 1214--1217, 2009.

%57
\bibitem{Adouane16}
Vilca J., Adouane L., Mezouar Y.:
\newblock {\em {Optimal Multi-Criteria Waypoint Selection for Autonomous Vehicle Navigation in Structured Environment}}. 
\newblock In: Journal of Intelligent and Robotic Systems 82(2): pp. 301--324, 2016.

%58
\bibitem{ECBS13}
Ramalho M., Lopes M., Sousa F., Marques H., Cordeiro L., Fischer B.:
\newblock {\em {SMT-Based Bounded Model Checking of C++ Programs} }.
\newblock In: International Conference on Engineering of Computer-Based Systems, pp. 147--156, 2013.

%59
\bibitem{Pereira15}
Pereira P.  Albuquerque H., Marques H., Silva I., Carvalho C., Santos V., Ferreira R., Cordeiro L.: 
\newblock {\em {Verifying CUDA Programs using SMT-Based Context-Bounded Model Checking}}.
\newblock In: ACM Symposium on Applied Computing, Software Verification and Testing Track, pp. 1648-1653, 2016.

%60
\bibitem{Sousa15}
Sousa F., Cordeiro L., Lima Filho E.: 
\newblock {\em { Bounded Model Checking of C++ Programs Based on the Qt Framework.}} 
\newblock In: Global Conference on Consumer Electronics, pp. 179--180, 2015.

%61
\bibitem{Beyer14}
D.~Beyer 
\newblock {\em {Status report on software verification - (competition summary {SV-COMP})}}. 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 8413, pp. 373--388, 2014.

%62
\bibitem{BeyerSVCOMP15}
D.~Beyer:
\newblock {\em {Software Verification and Verifiable Witnesses - (Report on SV-COMP 2015).}} 
\newblock In: Tools and Algorithms for the Construction and Analysis of Systems, LNCS 9035, pp. 401-416, 2015.

%63
\bibitem{KahlonWG09}
Kahlon V., Wang C., Gupta A.:
\newblock {\em{Monotonic Partial Order Reduction: An Optimal Symbolic Partial Order Reduction Technique}}.
\newblock In: International Conference on Computer-Aided Verification, LNCS 5643, pp. 398--413, 2009.

%64
\bibitem{morse15}
J.~Morse.
\newblock {\em {Expressive and Efficient Bounded Model Checking of Concurrent Software}}.
\newblock {University of Southampton, PhD Thesis}, 2015.

%65
\bibitem{Inverso14}
Inverso O., Tomasco E., Fischer B., La Torre S., Parlato G.:
\newblock {\em {Bounded Model Checking of Multi-threaded C Programs via Lazy Sequentialization.}}
\newblock In: International Conference on Computer-Aided Verification, LNCS 8559, pp. 585-602, 2014.
